---
title: "Initial Data Exploration"
date: "Tuesday, February 10, 2015"
output:
  html_document: 
    theme: spacelab  
    highlight: tango
---

**Purpose**: To do an initial exploratory analysis to understand the data and provide insights into feature extraction.

```{r}
library(stringr)
library(reshape)
library(ggplot2)

```

## Iteration 1: Analysis with n = 2

Notes: 
* FileName1: 0A32eTdBKayjCWhZqDOQ ; Classification Class: 2  
* FileName2: 0ACDbR5M3ZhBJajygTuf; Classification Class: 7
* Filenames are char(20) in length

Getting the data
```{r, cache =TRUE}
# File 1
file_1_Meta <- readLines("../data/dataSample/0A32eTdBKayjCWhZqDOQ.asm")
file_1_Bin <- read.table(file = "../data/dataSample/0A32eTdBKayjCWhZqDOQ.bytes", header = F)

# File 2
file_2_Meta <- readLines("../data/dataSample/0ACDbR5M3ZhBJajygTuf.asm")
file_2_Bin <- read.table(file = "../data/dataSample/0ACDbR5M3ZhBJajygTuf.bytes", header = F)
```

Let's look at the contents  
```{r}
# Metadata file
head(file_1_Meta)
tail(file_2_Meta)

# Binary file
head(file_1_Bin)
tail(file_2_Bin)
```

Performing FFT on the Binary files

```{r, cache=TRUE}

# read in training labels
trainLabels <- read.table(file="../data/trainLabels.csv", sep=",", header=T)

# read in training data
trainFilenames <- list.files("../data/dataSample/", pattern="*.bytes", full.names=TRUE)

noTrain <- length(trainFilenames) # Maybe when n is large, might want to subStrRight

# variable to break the job into 1000 blocks
progressBlock <- 100

# variable to set the width of FFT analysis to keep
FFTWidth <-100

# create empty matrix to contain results
myFFT <- matrix(,nrow=noTrain,ncol=2*FFTWidth)
# label the matrix using the base part of the filenames
row.names(myFFT)=substr(trainFilenames,20,39)

for (i in 1:noTrain) {
    print(trainFilenames[i])

    # take FFT of the decimal values of the hex values in the .bytes file with 1st column (labels) removed
    thisFFT=fft(as.numeric(sprintf("%d",unlist(read.table(trainFilenames[i])[,2:17], use.names=FALSE))))[1:FFTWidth]

     # separate out the resulting complex numbers into amplitude and phase parts and store them separately
    myFFT[i,1:FFTWidth]=Mod(thisFFT)
    myFFT[i,(FFTWidth+1):(2*FFTWidth)]=Arg(thisFFT)

    # check on progress and dump results so far if it's warranted
    if ((i %% progressBlock) == 0) {
      print(i)
      # write out a copy of the results so we can restart if it crashes
      write.table(myFFT,file="FFTResults.txt",sep='\t',row.names=TRUE)
    }
}
# dump final results
write.table(myFFT,file="FFTResults.txt",sep='\t',row.names=TRUE)

```


Graphing the results
```{r}
FFTResults <- read.table("FFTResults.txt")
FFTResults$name <- row.names(myFFT)

meltFFTResults <- melt(FFTResults, id ="name")


g <- ggplot(meltFFTResults, aes(x=variable, y=value, color = name)) + geom_point() + geom_density()
print(g)

```


